environmental_data_preperation

### 2018-09-10 src/environmental_data_preperation.Rmd
wel...not really much progress..

# read in a netcdf
```{r}
library("RNetCDF") #this will read the netcdf version 1 formats 
ncpath <- "../data/env/"
ncname <- "CMEMS_GLOBAL_REANALYSIS_PHY_001_025_salinity_monthly_mean_1993-01.nclonlat.ncdepthtrim"  
ncfname <- paste(ncpath, ncname, ".nc", sep="")
dname <- "salinity"  
ncin <- nc_open(ncfname)
ncin
```
# convert netCDF into a raster brick

```{r}
library(raster)
rp <- projectRaster(ncin,crs="+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m no_defs")
```

```{r}
ncbrick <- brick(ncin)
```

>>>>

# read in a netcdf
```{r}
library("RNetCDF") #this will read the netcdf version 1 formats 
library(ncdf4)
ncbr <- brick("../data/env/CMEMS_GLOBAL_REANALYSIS_PHY_001_025_salinity_monthly_mean_1993-01.nclonlat.ncdepthtrim.nc")
ncbr
```

reproject...
```{r}
canada_eq_ar_proj <- "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
library(rgdal)
rp <- projectRaster(ncbr, crs = canada_eq_ar_proj)
rp
```
